\documentclass[12pt]{article}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{hyperref}
\usepackage{booktabs}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}

\title{The $W(3,3)$ Graph: Uniqueness, Tau Values,\\
       and the CM $j$-Tower}
\author{Wil Dahn}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
The Ramanujan bipartite graph $W(3,3)$ of Lubotzky--Phillips--Sarnak is
characterized among the family $W(3,q)$ by six simultaneous algebraic
coincidences (C1--C6), each proved symbolically.
The spectral parameters encode the Ramanujan tau function at the first two primes:
$\tau(2)=-f(3)=-24$ and $\tau(3)=k(3)\Phi_6(3)\cdot 3=252$.
The $j$-invariants of all CM orders attached to the Ihara zeta sectors of $W(3,3)$
are perfect cubes of graph parameters, forming a five-entry tower
$\{k^3,\,-g^3,\,(v/2)^3,\,-\Sigma^3,\,255^3\}$ with $\Sigma=2^{\Phi_4/2}$;
this tower is generated entirely by the $s$-eigenspace sector, whose CM discriminant
$-4\Phi_6=-28$ is Heegner while the $r$-eigenspace discriminant $-4\Phi_4=-40$
has class number $2$. The sixth coincidence C6 --- that $3\mid g(3)$ uniquely
among prime $q$ --- makes $\Sigma=2^{g/3}$ an integer and links the $D=-11$
$j$-tower entry to the $r$-sector parameter $\Phi_4$ via $g/3=\Phi_4/2$.
As a physics application, the $W(3,3)$ spectral descent map predicts
a quasi-degenerate neutrino mass entry point $\mu_{\rm eff}^2=1/4$ and
seesaw cascade ratio $r=0.52244$. All results are verified by
$\mathbf{456}$ automated unit tests~\cite{Dahn2026repo}.
\end{abstract}

\tableofcontents
\bigskip

%%% INTRODUCTION %%%
\section*{Introduction}
\addcontentsline{toc}{section}{Introduction}
\label{sec:intro}

The Lubotzky--Phillips--Sarnak graph $W(3,3)$ is the unique member of the
infinite family $\{W(3,q)\}_{q\equiv 1(4)}$ for which the following six
algebraic coincidences hold simultaneously:
\begin{itemize}
\item[\textbf{C1.}] The $r$-eigenvalue discriminant equals $-4\Phi_4$:
  the eigenvalue equation $\mathrm{ev}_r^2-4(k-1)=-4\Phi_4$ holds only at $q=3$.
\item[\textbf{C2.}] $k+g = q^q=27$: degree plus $s$-multiplicity equals $3^3$.
\item[\textbf{C3.}] $-f=\tau(2)=-24$ and $kq\Phi_6=\tau(3)=252$:
  the spectral multiplicities encode the Ramanujan tau function at the first two primes.
\item[\textbf{C4.}] $\Phi_6(3)=7$ is a Heegner number:
  the CM field $\mathbb{Q}(\sqrt{-7})$ of the $s$-sector has class number $1$.
\item[\textbf{C5.}] $a_{k-1}(E)=\mathrm{ev}_s$: the Frobenius trace at $p=k-1=11$
  on the CM curve $E\colon y^2=x^3-35x+98$ ($j=-g^3$) equals the $s$-eigenvalue.
\item[\textbf{C6.}] $3\mid g(3)$: among all prime $q$, only $q=3$ has $3\mid g(q)$,
  making $\Sigma=2^{g/3}=2^{\Phi_4/2}$ an integer spectral invariant.
\end{itemize}
Together C1--C6 characterize $W(3,3)$ uniquely in $\{W(3,q)\}$
(Theorems~\ref{thm:uniqueness}--\ref{rem:C6}).

A consequence of C4--C6 is a five-entry \emph{$j$-tower}: the $j$-invariants
of all CM orders attached to the Ihara zeta sectors are perfect cubes of graph
parameters, $\{k^3,-g^3,(v/2)^3,-\Sigma^3,P^3\}$ with $P=255$
(Proposition~\ref{prop:cube}). No Heegner discriminant with $|D|>4\Phi_6=28$
contributes a cube root to the $W(3,3)$ spectral ring.

As a physics application (Sections~\ref{sec:neutrino}--\ref{sec:seesaw}),
the spectral descent map of $W(3,3)$ predicts a quasi-degenerate neutrino mass
entry point $\mu_{\rm eff}^2=1/4$ with seesaw cascade ratio $r=0.52244$,
in tension with the DESI DR1 bound $\sum m_\nu<72\,\mathrm{meV}$~\cite{DESI2024}.

All results are verified by $\mathbf{456}$ automated unit tests~\cite{Dahn2026repo}.

\medskip
\noindent\textit{Structure.}
\S\ref{sec:graph} defines $W(3,3)$ and its parameter table.
\S\ref{sec:uniqueness} proves C1--C5 symbolically.
\S\ref{sec:tau} establishes C3, C5--C6, the tau bridge, and the $j$-tower.
\S\S\ref{sec:neutrino}--\ref{sec:seesaw} develop the neutrino application.

%%% SECTION 1 %%%
\section{The Graph $W(3,3)$}
\label{sec:graph}

The Lubotzky--Phillips--Sarnak graph $W(3,q)$ \cite{LPS1988} is a
$k$-regular bipartite Ramanujan graph defined for prime powers
$q\equiv 1\pmod{4}$, with $k=q(q+1)$ and $|V|=2(q+1)(q^2+1)=2v$.
We work at $q=3$.

\begin{table}[h]
\centering
\begin{tabular}{lll}
\toprule
Parameter & Symbol & Value \\
\midrule
Degree              & $k=q(q+1)$          & $12$ \\
Vertices per side   & $v=(q+1)(q^2+1)$    & $40$ \\
$r$-eigenvalue      & $r=q-1$             & $2$ \\
$s$-eigenvalue      & $s=-(q+1)$          & $-4$ \\
$r$-multiplicity    & $f=q(q+1)^2/2$      & $24$ \\
$s$-multiplicity    & $g=q(q^2+1)/2$      & $15$ \\
$\Phi_3(q)=q^2+q+1$ & $\Phi_3$            & $13$ \\
$\Phi_4(q)=q^2+1$   & $\Phi_4$            & $10$ \\
$\Phi_6(q)=q^2-q+1$ & $\Phi_6$            & $7$ \\
$\Sigma=2^{\Phi_4/2}$& $\Sigma$            & $32$ \\
$P=q(\Phi_4/2)(\Phi_4{+}\Phi_6)$ & $P$ & $255$ \\
\bottomrule
\end{tabular}
\caption{Parameters of $W(3,3)$ at $q=3$.}
\end{table}

The Ihara zeta function is
\[
  \zeta_{W}(u)^{-1} = (1-u^2)^{k(v-1)/2}\,p_1(u)^f\,p_2(u)^g,
\]
with $p_1(u)=1-2u+11u^2$, $p_2(u)=1+4u+11u^2$,
and discriminants $\mathrm{disc}(p_1)=-4\Phi_4=-40$,
$\mathrm{disc}(p_2)=-4\Phi_6=-28$.

%%% SECTION 2 %%%
\input{section2_uniqueness}

%%% SECTION 3 %%%
\input{section3_tau_bridge}

%%% SECTION 4 %%%
\section{Neutrino Mass Constraint}
\label{sec:neutrino}

For a neutrino mass vector $\mathbf{m}=(m_1,m_2,m_3)$ normalized to $m_{\max}=1$,
define
\[
  \mu_{\rm eff}^2(\mathbf{m}) = -\frac{\ln(\prod_i m_i/m_{\max})^{1/3}}{\ln\Phi_4}.
\]

\begin{theorem}[Entry point]
The $W(3,3)$ spectral constraint $\mu_{\rm eff}^2=1/(q+1)=1/4$
has a unique solution $m_1=m_1^*$ for each neutrino mass ordering.
Under the normal hierarchy with NuFIT 5.3 oscillation parameters \cite{NuFIT53},
$m_1^*\approx 50.7\,\mathrm{meV}$ and $\sum m_\nu\approx 167\,\mathrm{meV}$.
\end{theorem}

\begin{corollary}[DESI consistency]
The DESI DR1 bound $\sum m_\nu < 72\,\mathrm{meV}$ \cite{DESI2024}
excludes the NH entry point at greater than $2\sigma$.
The $W(3,3)$ spectral constraint predicts quasi-degenerate neutrinos
in tension with current cosmological data.
\end{corollary}

%%% SECTION 5 %%%
\section{The Seesaw Cascade}
\label{sec:seesaw}

Define the seesaw map $T\colon\mu\mapsto\mu_{\rm eff}^2(1/\mathbf{m}(\mu))$.

\begin{theorem}[Cascade ratio]\label{thm:cascade}
In the quasi-degenerate NH limit,
\[
  r = \frac{\Delta m^2_{21}+\Delta m^2_{31}}{2\Delta m^2_{31}-\Delta m^2_{21}}
  \;\xrightarrow{\Delta m^2_{21}\to 0}\;\frac{1}{2},
  \qquad r-\tfrac{1}{2} = \frac{3\Delta m^2_{21}}{2(2\Delta m^2_{31}-\Delta m^2_{21})}.
\]
With NuFIT 5.3 values~\cite{NuFIT53}: $r=0.52244$.
\end{theorem}
\begin{proof}
Expand $\mu_{\rm eff}^2$ to leading order in $\Delta m^2/m_1^2$;
the ratio $r=B/A$ with $A=(\Delta m^2_{31}/3-\Delta m^2_{21}/6)/\ln\Phi_4$
and $B=(\Delta m^2_{21}+\Delta m^2_{31})/(6\ln\Phi_4)$.
$\Phi_4$ cancels; $r-1/2=3A'/(2(2B'-A'))$ follows algebraically.
\end{proof}

The first cascade iterates land near $W(3,3)$ values:
$T^0=1/4=1/m$, $T^1\approx 1/\Phi_6$, $T^2\approx 1/\Phi_3$;
asymptotically $T^{n+1}/T^n\to r$.

\begin{thebibliography}{99}
\bibitem{LPS1988}
  A.~Lubotzky, R.~Phillips, P.~Sarnak,
  \emph{Ramanujan graphs},
  Combinatorica \textbf{8} (1988), 261--277.

\bibitem{Deligne1974}
  P.~Deligne,
  \emph{La conjecture de Weil I},
  Publ.\ Math.\ IHES \textbf{43} (1974), 273--307.

\bibitem{LMFDB}
  The LMFDB Collaboration,
  \emph{The $L$-functions and Modular Forms Database},
  \texttt{https://www.lmfdb.org}, 2024.

\bibitem{NuFIT53}
  I.~Esteban, M.~C.~Gonzalez-Garcia, M.~Maltoni, T.~Schwetz, A.~Zhou,
  JHEP \textbf{09} (2020) 178; \texttt{http://www.nu-fit.org}.

\bibitem{DESI2024}
  DESI Collaboration,
  \emph{DESI 2024 VI: Cosmological constraints from BAO},
  arXiv:2404.03002.

\bibitem{Dahn2026repo}
  W.~Dahn,
  \emph{$W(3,3)$-Theory: Automated tests and computations},
  \texttt{https://github.com/wilcompute/W33-Theory}, 2026.
\end{thebibliography}

\end{document}
